Density dependence

### 2020-09-23 R/density dependence.Rmd
switched analysis to use coordinate based competition.

I don't know what a height of 0 means...
Height of 0 probably means it was knocked over, or very small, or dead.

@@

```{r}
mpois <- glmer(shts_next ~ log_shts + habitat + density_0_10 + density_10_20 + (1|ha_id_number) + (1|year_post),
                family = poisson(link = "log"),
                data = ha_sub)

@@

mnorm <- glmer(shts_next ~ log_shts + habitat + density_0_10 + density_10_20 + (1|ha_id_number) + (1|year_post),
                family = gaussian(link = "log"),
                data = ha_sub)
```

@@

```{r}
x<-check_heteroscedasticity(m_growth)
plot(x)
```

@@

```{r}
m_growth2 <- glmer(shts_next ~ log_shts + habitat + density_0_10 + density_10_20 + (1|year_post),
               family = gaussian(link = "log"),
               data = ha_sub)
AICtab(m_growth, m_growth2)
```

@@

```{r}
m_growth3 <- glmer(shts_next ~ log_shts + habitat + density_0_10 + density_10_20 + (1|ha_id_number),
               family = gaussian(link = "log"),
               data = ha_sub)
AICtab(m_growth, m_growth2, m_growth3)
```

@@

```{r}
Anova(m_growth)
```

Odd, density further out is significant, but density close is not.

```{r}
fixef(m_growth)
```

Both weakly positive density dependence

@@

```{r}
m_surv <- glmer(surv ~ log_shts + habitat + density_0_10 + density_10_20 + (1|ha_id_number) + (1|year), 
                family = binomial, data = ha_sub)
```

@@

```{r}
m_surv2 <- glmer(surv ~ log_shts + habitat + density_0_10 + density_10_20 + (1|year), 
                family = binomial, data = ha_sub)
AICtab(m_surv, m_surv2)
```

@@

```{r}
m_surv3 <- glm(surv ~ log_shts + habitat + density_0_10 + density_10_20, 
                family = binomial, data = ha_sub)
AICtab(m_surv2, m_surv3)
```
Can't remove year.

@@

@@

```{r}
ha_sub <- 
  ha_sub %>% 
  mutate(flwr = as.integer(infl>0), .before = infl)

@@

```{r}
m_flwr <- glmer(flwr ~ log_shts + habitat + density_0_10 + density_10_20 + (1|ha_id_number) + (1|year),
                family = binomial, data = ha_sub)
```

@@

```{r}
m_flwr2 <- glmer(flwr ~ log_shts + habitat + density_0_10 + density_10_20 + (1|year),
                 family = binomial, data = ha_sub)
AICtab(m_flwr, m_flwr2)
```
Can't remove plant ID.

```{r}
m_flwr3 <- glmer(flwr ~ log_shts + habitat + density_0_10 + density_10_20 + (1|ha_id_number),
                 family = binomial, data = ha_sub)
AICtab(m_flwr, m_flwr2, m_flwr3)
```

@@

Ok, there's an effect, but oddly only past 20m.  Again, positive density dependence.

@@

@@

@@

```{r}
Q <-
  ha_sub %>%
  select(density_0_10:density_50_60) %>% 
  as.matrix()

@@

```{r}
library(dlnm)
library(mgcv)

@@

@@

```{r}
x <- crosspred("Q", model = g_growth, cumul = TRUE)
summary(x)
```

@@

```{r}
plot.crosspred(x,
               ptype = "contour",
               xlab = "#shoots/100m^2",
               ylab = "distance (m)",
               cumul = FALSE)
```
So this shows negative density dependence that seems to be strongest at about 40-50 m away from the focal plant.

@@

```{r}
plot.crosspred(x, ptype = "slice", var = 100, xlab = "distance (m)", main = "Effect of 100 shoots/100m^2")
plot.crosspred(x, ptype = "slice", var = 10, xlab = "distance (m)", main = "Effect of 10 shoots/100m^2")
```

@@

```{r}
plot(x, ptype = "overall", xlab = "density (shoots/100m^2)", cumul = TRUE)
```

@@

```{r}
#use arglag to override lag dimension of crossbasis, use argvar to override plant density dimension.
lin <- dlnm:::lin
xt <- list(bs = "cr", arglag = list(fun = "lin"))

@@

```{r}
x <- crosspred("Q", model = g_growth)
plot.crosspred(x, ptype = "contour", xlab = "#shoots/100m^2", ylab = "distance (m)")

@@

```{r}
anova(g_growth)
```

>>>>

Technically, the density data are only for 2006, 2007, and 2009, so I should really only use those three transition years.  This might still not be 100% correct.

```{r}
ha_sub_sub <-
  ha_sub %>% 
  filter(year %in% c(2006, 2007, 2009))
```

@@

```{r}
mpois <- glmer(shts_next ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number) + (1|year_post),
                family = poisson(link = "log"),
                data = ha_sub)

@@

mnorm <- glmer(shts_next ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number) + (1|year_post),
                family = gaussian(link = "log"),
                data = ha_sub)
```

@@

```{r}
x <- check_heteroscedasticity(m_growth)
plot(x)
```

@@

```{r}
m_growth2 <- glmer(shts_next ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|year_post),
               family = gaussian(link = "log"),
               data = ha_sub)
AICtab(m_growth, m_growth2)
```

@@

```{r}
m_growth3 <- glmer(shts_next ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number),
               family = gaussian(link = "log"),
               data = ha_sub)
AICtab(m_growth, m_growth2, m_growth3)
```

@@

```{r}
Anova(m_growth)
fixef(m_growth)
```

Positive density dependence at 0--5 meters

Same for 3-year subset?

```{r}
mgrowth_sub <- glmer(shts_next ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number) + (1|year_post),
                family = gaussian(link = "log"),
                data = ha_sub_sub)
Anova(mgrowth_sub)
```

No longer significant.

@@

```{r}
m_surv <- glmer(surv ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number) + (1|year), 
                family = binomial, data = ha_sub)
```

@@

```{r}
m_surv2 <- glmer(surv ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|year), 
                family = binomial, data = ha_sub)
AICtab(m_surv, m_surv2)
```

@@

```{r}
m_surv3 <- glm(surv ~ log_shts + habitat + shts_0_5 + shts_5_10, 
                family = binomial, data = ha_sub)
AICtab(m_surv2, m_surv3)
```
Can't remove year.

@@

Does this hold for the 3-year subset?

```{r}
m_surv2_sub <- glmer(surv ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|year), 
                family = binomial, data = ha_sub_sub)
Anova(m_surv2_sub)
```

No longer significant

@@

```{r}
ha_sub <- 
  ha_sub %>% 
  mutate(flwr = as.integer(infl > 0), .before = infl)

@@

```{r}
m_flwr <- glmer(flwr ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number) + (1|year),
                family = binomial, data = ha_sub)
```

@@

```{r}
m_flwr2 <- glmer(flwr ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|year),
                 family = binomial, data = ha_sub)
AICtab(m_flwr, m_flwr2)
```
Can't remove plant ID.

```{r}
m_flwr3 <- glmer(flwr ~ log_shts + habitat + shts_0_5 + shts_5_10 + (1|ha_id_number),
                 family = binomial, data = ha_sub)
AICtab(m_flwr, m_flwr2, m_flwr3)
```

@@

Ok, there's an effect, but oddly only at the further distance.  Again, positive density dependence.

@@

No flowering data for 2006, 2007, and 2009.  These models won't run if the data are subset to only include these years.

@@

**Not working yet**

@@

```{r eval=FALSE}
Q <-
  ha_sub %>%
  select(density_0_10:density_50_60) %>%
  as.matrix()

@@

```{r eval=FALSE}
library(dlnm)
library(mgcv)

@@

```{r eval=FALSE}
g_surv <-
  gam(surv ~ s(log_shts) +
        habitat +
        s(Q, L,
          bs = "cb",
          k = c(5, 4),
          xt = list(bs = "cr")),
      family = binomial,
      data = ha_sub,
      method = "REML")
```

@@

```{r eval=FALSE}
# x <- crosspred("Q", model = g_surv, cumul = TRUE)
x <- crosspred("Q", model = g_growth, cumul = TRUE)
summary(x)
```

@@

```{r eval=FALSE}
plot.crosspred(x,
               ptype = "contour",
               xlab = "#shoots/100m^2",
               ylab = "distance (m)",
               cumul = FALSE)
```
So this shows negative density dependence on growth that seems to be strongest at about 40-50 m away from the focal plant.

@@

```{r eval=FALSE}
plot.crosspred(x, ptype = "slice", var = 100, xlab = "distance (m)", main = "Effect of 100 shoots/100m^2")
plot.crosspred(x, ptype = "slice", var = 10, xlab = "distance (m)", main = "Effect of 10 shoots/100m^2")
```

@@

```{r eval=FALSE}
plot(x, ptype = "overall", xlab = "density (shoots/100m^2)", cumul = TRUE)
```

@@

```{r eval=FALSE}
#use arglag to override lag dimension of crossbasis, use argvar to override plant density dimension.
lin <- dlnm:::lin
xt <- list(bs = "cr", arglag = list(fun = "lin"))

@@

```{r eval=FALSE}
x <- crosspred("Q", model = g_growth)
plot.crosspred(x, ptype = "contour", xlab = "#shoots/100m^2", ylab = "distance (m)")

@@

```{r eval=FALSE}
anova(g_growth)
```
